### 2015-12-09 paper/4-performance.tex
Wrote brief introduction to performance section

%TODO say that you will now prove your claims about the aproach having nearly no impact
%TODO and potentially even claim that you are faster than adevs for some situations, due to the algorithms from PythonPDEVS and further features
%TODO briefly give some hardware info on the machine (CPU, OS, RAM), used software (version of adevs, GCC, ...), and about number of samples/variance
\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
In our benchmarks, we will consistently compare the performance of dxex with adevs. The implemented models for the each benchmark are functionally identical.\\
Dxex uses integer timestamps whereas adevs uses floating point time representation. Tests show there is little difference performance-wise (both types fit in a machine word).\\
The benchmarks have been compiled using the {\tt -O3} option and link-time optimization, with all IO disabled. To compare the models in details, we have run the different benchmarks with different parameters.\\
The benchmarks have been run on a i7-2670QM, 16GiB RAM, Arch Linux (4.2.5 kernel) and G++ 5.2. Interpretation of the benchmark results is done using call-graphs generated by perf. A selection of those call-graphs is available in the code repository. For the runtime plots, perf is used in combination with R.\\
%Note that a fixed timeadvance (e.g. devstone) is set at 100.
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical. As can be seen in Figure~\ref{fig:Devstone}, dxex is outperforming adevs considerably. This can be explained by the fact that, using Direct connection, the hierharchical structure is being flattened whereas, in the adevs case, considerable overhead is caused by traversing the coupled model's structure to pass events.
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\caption{Devstone}
	\label{fig:Devstone}
\end{figure}

>>>>

In this section, we evaluate the performance of our simulation tool.
We show that the inclusion of multiple synchronization protocols does not decrease our performance to the point where it is unusable.
To this end, we compare to adevs, one of the most efficient simulation kernels at this time~\cite{DEVSSurvey}.
A comparison is made for both the CPU and memory usage of both sequential simulation and parallel simulation.

We start of with a comparison of sequential simulation, to show how adevs and dxex relate in this simple case.
We not only show that our approach does not influence performance negatively, but also that our main simulation algorithm, similar to the one of PythonPDEVS, is significantly faster than the one found in adevs.
Similar differences, compared to adevs, can also be seen in the parallel simulation benchmarks.
In the parallel simulation benchmarks, the benefit of our different synchronization protocols is also indicated.

For all benchmarks, results were all well within 1\% deviation of the average, such that only the average is used in the remainder of this section.
The same compilation flags were used for both adevs and dxex benchmarks (``\texttt{-O3}'').
To guarantee comparable results, no IO was performed during the benchmarking phase.
Simulation traces were used to verify that both adevs and dxex models have exactly the same behaviour.

\subsection{Sequential Simulation}
%TODO we start with sequential simulation results, because this is still base case
%TODO compare CPU time with adevs for some benchmarks
%TODO and explain why there is such a difference
%TODO (spend some time here, as this is also important)
In our benchmarks, we will consistently compare the performance of dxex with adevs. The implemented models for the each benchmark are functionally identical.\\
Dxex uses integer timestamps whereas adevs uses floating point time representation. Tests show there is little difference performance-wise (both types fit in a machine word).\\
The benchmarks have been compiled using the {\tt -O3} option and link-time optimization, with all IO disabled. To compare the models in details, we have run the different benchmarks with different parameters.\\
The benchmarks have been run on a i7-2670QM, 16GiB RAM, Arch Linux (4.2.5 kernel) and G++ 5.2. Interpretation of the benchmark results is done using call-graphs generated by perf. A selection of those call-graphs is available in the code repository. For the runtime plots, perf is used in combination with R.\\
%Note that a fixed timeadvance (e.g. devstone) is set at 100.
\subsubsection{Devstone}
The Devstone \cite{DEVStone} benchmark is highly hierarchical. As can be seen in Figure~\ref{fig:Devstone}, dxex is outperforming adevs considerably. This can be explained by the fact that, using Direct connection, the hierharchical structure is being flattened whereas, in the adevs case, considerable overhead is caused by traversing the coupled model's structure to pass events.
\begin{figure}[h]
	\includegraphics[width=.5\textwidth]{fig/fig1.eps}
	\caption{Devstone}
	\label{fig:Devstone}
\end{figure}
